---
title: "ANES Clean"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
```

# Important variables

* weight variables
** VCF0009x/VCF0009y/VCF0009z

* demographics
** VCF0101 - age
** VCF0102 - age group
** VCF0104 - gender
** VCF0110 - R education 4-cat
** VCF0114 - R family income group
** VCF0140 - education 6-cat
** VCF0140a - R education 7-cat
** VCF0105a - Race/ethnicity summary 7-cat
** VCF0105b - Race/ethnicity summary 4-cat
** VCF0106 - Race summary 3-cat
** VCF0301 - Party Identification of Respondent
** VCF0302 - Initial Party ID response
** VCF0305 - strength of partisanship


* analysis
** VCF0201 - FT Democrats
** VCF0202 - FT Republicans
** VCF0203 - FT Protestants
** VCF0204 - FT Catholics
** VCF0205 - FT Jewish people
** VCF0206 - FT Black people
** VCF0207 - FT White people
** VCF0208 - FT Southerners
** VCF0211 - FT Liberals
** VCF0212 - FT Conservatives
** VCF0217 - FT Chicanos/Hispanics
** VCF0219 - FT Middle class people
** VCF0220 - FT People on welfare
** VCF0223 - FT Poor people
** VCF9006 - FT Women
** VCF0227 - FT Asian Americans
** VCF0233 - FT Illegal Aliens
** VCF0232 - FT Gays and lesbians

** VCF0839 - Gov Services/Spending scale
** VCF0843 - Gov Defense Spending
** VCF0886 - Fed Spend poor people
** VCF0887 - Fed Spend child care
** VCF0888 - Fed spend dealing with crime
** VCF0889 - Fed spend fight AIDS
** VCF0890 - Fed spend public school
** VCF0891 - Fed spend aid for college students
** VCF0892 - Fed spend foreign aid
** VCF0893 - Fed spend the homeless
** VCF0894 - Fed spend welfare
** VCF9048 - Fed spend space/science/technology
** VCF9047 - Fed spend improve/protect the environment
** VCF9046 - Fed spend food stamps
** VCF0879 - Increase/decrease number of immigrants to the US 6-cat
** VCF0879a - Increase/decrease number of immigrants to the US 4-cat





```{r, echo=FALSE}
var_anes <- read_anes_cdf %>%
  select(year = VCF0004, id = VCF0006a,
    # weight variables
    weight1 = VCF0009x, weight2 = VCF0009y, weight3 = VCF0009z,
    # demographic variables
    age = VCF0101, age_group = VCF0102, gender = VCF0104, educ4 = VCF0110, fam_income = VCF0114,
    educ6 = VCF0140, educ7 = VCF0140a, race7 = VCF0105a, race4 = VCF0105b, race3 = VCF0106, 
    partyid = VCF0301, party = VCF0302, id_strength = VCF0305, 
    # group thermometer variables
    ft_dem =  VCF0201, ft_rep = VCF0202, ft_protestants = VCF0203, ft_catholic = VCF0204, 
    ft_jewish = VCF0205, ft_black = VCF0206, ft_white = VCF0207, ft_south = VCF0208, 
    ft_lib = VCF0211, ft_conserv = VCF0212, ft_hispanic = VCF0217, ft_middle = VCF0219, 
    ft_welfare = VCF0220, ft_poor = VCF0223, ft_women = VCF9006, ft_asian = VCF0227, 
    ft_undoc = VCF0233, ft_gay = VCF0232, 
    # opinion variables
    serv_spend = VCF0839, spend_def = VCF0843, spend_poor = VCF0886, spend_child = VCF0887, 
    spend_crime = VCF0888, spend_aids = VCF0889, spend_school = VCF0890, spend_college = VCF0891, 
    spend_foreign = VCF0892, spend_homeless = VCF0893, spend_welfare = VCF0894, spend_sci = VCF9048, 
    spend_environ = VCF9047, spend_stamps = VCF9046, immigrants6 = VCF0879, immigrants4 = VCF0879a)
```

Select years for study

```{r, echo=FALSE}
# new data set to filter years
anes_recent <- var_anes

# make a numeric variable of years to study
years <- c(2004, 2008, 2012, 2016)

# filter year variable for the numbers contained in the years vector
anes_recent <- anes_recent[anes_recent$year == years, ]

# make year variable into a factor
anes_recent$year <- as.factor(anes_recent$year)
```
 


```{r, echo=FALSE}
# copy this for code chunk
```

